### 2020-08-16 evaluation.tex
9 pages

In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio(PSNR) to evaluate the accuracy of the recovered images. The results are shown in Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}. Optical Character Recognition (OCR) services are also utilized to evaluate the accuracy. The model with traditional lens without optical zoom (hereafter referred as traditional lens) is trained and tested at 1-2 meters range, while the lens with optical zoom (hereafter referred as optical lens) at 5-7.5 meters, at which distance less than 5\% of the characters (only the simplest ones) can be recognized by humans from the photos without the assistance of SR algorithms. The PSNR and OCR results are shown in Fig. ~\ref{fig-control-1}.

This model can achieve an OCR accuracy above 90\% at 1.8m with traditional lens and at 6m with optical lens. Performances are relatively consistent in both day and night time, while increased distances mean less data and less restrictions of the possible outputs, which leads to artifacts (missing or misplaced strokes, etc.). It is the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixel-wise error rises steadily with the increased distance, the accuracy will experience a drastic drop.

@@

We observed that variations in light and angle parameter in training data is crucial to a robust model. In the tradition lens group, variations in distance is not so influential to the results, given that the distances are between 1 and 2 meters. Distance changes do not have such a large impact on the size of the characters shown in the images, so that features extracted from a fixed distance might still exist when these characters vary slightly in size. However, if the network is not exposed to angled images during the training process, the rotations and deformations caused by these angles will easily disturb the feature extraction process. The optical lens group yields similar results except the distance group. As the distance between phones are increased to 6 meters, increases in distance leads to greater complexity of image blurriness and less information, so that the model becomes more sensitive to distance changes.
% \begin{figure}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
%     \hfill
%     \caption{Performance for the adapting ability using traditional lens and optical lens.}
%     \label{fig:adapting}
% \end{figure}

\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results. We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level average. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution (VideoSR). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noisy and deformed patterns, while VideoSR approaches rely upon consistency between frames, so they fail to give satisfactory results. We used the relatively easy 'daytime 1.2m-distance direct with traditional lens' group of data for testing. The results are shown in Table~\ref{table-comp}.
\begin{table}[!t]
    \centering
    \caption{Comparison with existing systems.}
    \begin{tabular}{@{}cccc@{}}
        \toprule
    System & SRPeek & SRCNN & VideoSR \\ \midrule
    PSNR & 13.32db & 7.69db & 8.403db\\ 
    OCR Accuracy & 100\% & 10\% & 23\%\\ \bottomrule
    \end{tabular}
    \label{table-comp}
\end{table}

@@

We build the system on smartphone and evaluate its performance in real-life environments (shown in Fig.~\ref{fig-reallife}). We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim. As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it is insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lens at 1-2m range. We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model. No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty. The results are shown in Table~\ref{table-scenarios}.
\begin{figure}
	\centering
	\includegraphics[width=0.80\linewidth]{pic/reallife.pdf}
    \caption{Illustration of our real-life scenario (Distance between attacker and victim is shortened for demonstration).}
	\label{fig-reallife}
\end{figure}

@@

We can see that with the existence of tremors, the recognition accuracy drops from 95\% to 85\%/80\% for both OCR tools and human. We conclude from the results that hand tremors can impact the performance of our system. Although the edges of the phone are notable marks for image alignment, small shifts in the sub-pixel level will cause blurriness in the results of the networks, lowering the readability of the outputs.

\subsection{Success rate in different tasks}
We test the success rate of obtaining crucial information when the observed participant performs several tasks on a phone: reading text message, typing text message, entering PIN, and typing password with numbers, English and special characters. The observed participant will turn off the screen of his phone as soon as he/she finishes the task, while the observing participant will observe through our APP, constantly capturing images and processing them to display a real-time and magnified view of the observed phone. For the first two tasks, we ask the observing participant several questions to test if he/she have collected the vital information (e.g. the name or the location mentioned in the text). For the task of recognizing PIN and passwords, we use accuracy per character as a supplementary evaluation metric. In these two scenarios, we ignore the virtual keyboard and view only the textbox, assuming that the last character of the entered string is always visible. Fewer photos will be available for each character but deciphering English characters is also easier than Chinese characters, and we trained a model specifically for each task (with the same neural network architecture), the training images containing only English characters and numbers (or only numbers for the PIN entry scenario). The results are shown in Table~\ref{table-task}.

@@

We prove from this experiment that our system functions normally in everyday scenarios and poses a threat to screen privacy.

\subsection{Perceived shoulder surfing susceptibility}
We ask the observed participant to rate the perceived shoulder-surfing susceptibility in these scenarios. The attacker will be sitting or standing behind the participant at 1.8m range, pretending to be interacting with their own phone while continuously running the shoulder-surfing APP. None of the participants were alerted by the attacker's behavior and reported suspicion of shoulder-surfing. We believe that our system can enable a malicious attacker to gather large amounts of critical information from the victim while remaining unnoticed.

>>>>

In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio(PSNR) to evaluate the accuracy of the recovered images. The results are shown in Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}. Optical Character Recognition (OCR) services are also utilized to evaluate the accuracy. The traditional lens group is trained and tested at 1-2 meters distance, while the optical lens, 5-7.5 meters, where less than 5\% of the characters can be read with the naked eye. The PSNR and OCR results are shown in Fig. ~\ref{fig-control-1}.

This model can achieve an OCR accuracy above 90\% at 1.8m with traditional lens and at 6m with optical lens. Performances are relatively consistent in both day and night time, while increased distances mean less data, causing more artifacts(missing or misplaced strokes, etc.). It is the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixel-wise error rises steadily with the increased distance, the accuracy will experience a drastic drop.

@@

We observed that variations in light and angle parameter in training data is crucial to a robust model. In the tradition lens group, the variations within 1 and 2 meters may have a smaller impact to the size of the characters
 so that features extracted at one distance might still exist at another.
 However, tilts and angles cause rotations and deformations and severely disturb the feature extraction process. The optical lens group yields similar results except at variations in distance. At a range of 6 meters, increases in distance leads to greater complexity of image blurriness, leading to more complex feature extraction and a more fragile model.
% \begin{figure}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
%     \hfill
%     \caption{Performance for the adapting ability using traditional lens and optical lens.}
%     \label{fig:adapting}
% \end{figure}

\subsection{Comparison with other architectures}
We train and test other widely used networks with the same sets of data and evaluate their results. We chose SRCNN, a commonly used single image SR network, applying it to each single image before merging the results by pixel-level average. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution (VideoSR). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noisy and deformed patterns, while VideoSR approaches rely upon consistency between frames, so they fail to give satisfactory results. We used the relatively easy 'daytime 1.2m-distance direct with traditional lens' group of data for testing. The results are shown in Table~\ref{table-comp}.
\begin{table}[!t]
    \centering
    \caption{Comparison with existing systems.}
    \begin{tabular}{@{}cccc@{}}
        \toprule
    System & SRPeek & SRCNN & VideoSR \\ \midrule
    PSNR & 13.32db & 7.69db & 8.403db\\ 
    OCR Accuracy & 100\% & 10\% & 23\%\\ \bottomrule
    \end{tabular}
    \label{table-comp}
\end{table}

@@

We build the system on smartphone and evaluate its performance in real-life scenarios (shown in Fig.~\ref{fig-reallife}). We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels, no optical zooming) for the attacker and a HUAWEI Mate8 smartphone for the victim, with the former ``1.8m daytime'' setting. We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model. No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty. The results are shown in Table~\ref{table-scenarios}.
\begin{figure}
	\centering
	\includegraphics[width=0.80\linewidth]{pic/reallife.pdf}
    \caption{Illustration of our real-life scenario (Distance between attacker and victim is shortened for demonstration).}
	\label{fig-reallife}
\end{figure}

@@

We can see that with the existence of tremors, the recognition accuracy drops from 95\% to 85\%/80\% for both OCR tools and human. We conclude from the results that hand tremors can impact the performance of our system. Hand tremors can cause motion blur and erratic shifts in the sub-pixel level(after image alignment phase) and impact performance.

\subsection{Success rate in different tasks}
We test the success rate of obtaining crucial information when the observed participant performs several tasks on a phone: reading text message, typing text message, entering PIN, and typing password with numbers, English and special characters(typing at 2 characters per second). We use accuracy per character as evaluation metric. In the PIN and password tasks, fewer photos will be available, but deciphering English characters is also easier than Chinese characters, and we use specifically trained models(with same structure and different training data). The results are shown in Table~\ref{table-task}.

@@

We conclude that \textsf{SRPeek} functions normally in everyday scenarios and poses a threat to screen privacy.

\subsection{Perceived shoulder surfing susceptibility}
We ask the participants to rate the perceived shoulder-surfing susceptibility after the experiment. The attacker sits or stands at 1.8m range, pretending to be interacting with their own phone while continuously running the shoulder-surfing APP. None of the participants reported suspicion of shoulder-surfing. We believe that our system can enable a malicious attacker to gather large amounts of critical information from the victim while remaining unnoticed.

### 2020-08-16 introduction.tex
minor
cl
9 pages

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/illustration.pdf}
    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm.}
	\label{overview}
\end{figure}

@@

\begin{itemize}

@@

\vspace{1mm}
\noindent
\textbf{Summary of Evaluation Results.}
Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's screen with above 90\% accuracy at 1.8m distance on a smartphone without optical zooming, or 6m on a phone with optical zooming in our experimental settings. \textsf{SRPeek} can capture snapshots and produce high-resolution images constantly with about 2 seconds interval. Our experiments in real life scenarios show that it can decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a serious threat to screen privacy.

\vspace{1mm}
\noindent
\textbf{Contributions.} This paper makes the following contributions:
\begin{itemize}
  \item	We propose \textsf{SRPeek}, an end-to-end threat model of shoulder surfing from a broad range, which can be deployed on commercial smartphones. To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
  \item	We design a multi-frame SR neural network architecture to reconstruct massive extremely blurred and defocused snapshots. It can be further extended to other text-recognition applications.
  \item	We evaluate this new shoulder surfing threat model in multiple scenarios. And it outperforms the state-of-the-arts for content recognition, calling for the new privacy concern.
\end{itemize}
% describe the organization of the paper

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.80\linewidth]{pic/illustration.pdf}
    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm.}
	\label{overview}
\end{figure}

@@

\begin{itemize}[leftmargin=*]

@@

\vspace{1mm}
\noindent
\textbf{Summary of Evaluation Results.}
Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's screen with above 90\% accuracy at 1.8m distance on a smartphone without optical zooming(hereafter referred as traditional lens), or 6m on a phone with optical zooming(hereafter referred as optical lens) in our experimental settings. \textsf{SRPeek} can capture snapshots and produce high-resolution images constantly with about 2 seconds interval. Our experiments in real life scenarios show that it can decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a serious threat to screen privacy.

\vspace{1mm}
\noindent
\textbf{Contributions.} This paper makes the following contributions:
\begin{itemize}[leftmargin=*]
  \item	We propose \textsf{SRPeek}, an end-to-end threat model of shoulder surfing from a broad range, which can be deployed on commercial smartphones. To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
  \item	We design a multi-frame SR neural network architecture to reconstruct massive extremely blurred and defocused snapshots. It can be further extended to other text-recognition applications.
  \item	We evaluate this new shoulder surfing threat model in multiple scenarios. And it outperforms the state-of-the-arts for content recognition, calling for the new privacy concern.
\end{itemize}
% describe the organization of the paper

### 2020-08-16 limitation_and_discussion.tex
cl
10.5pages
9 pages

\section{Limitations \& Discussions}
\label{sec-limitations-and-discussions}
There are certain limitations of this work. We require a certain degree of image capturing and processing abilities of the attacker's phone, and we also expect the victim not to exert too much disturbance to the target phone.
\vspace{1mm}
\noindent
\textbf{Image Capturing Ability}
Latest models of smartphones can capture images at 10 frames per second in burst mode easily, however, this ability is not common in phones that are 3 years old. Heavily used phones also perform less than ideal when capturing images in burst mode. Also, when capturing images, the user needs to hold their phone as still as possible to avoid motion blur and assist image alignment. The user also has to keep a sharp focus on the target phone.

@@

\vspace{1mm}
\noindent
\textbf{Motion and Tremors}
In our experiment we assume the observed user will hold still his/hers phone, and not making interactions too often. However, some users may tilt their phones during interactions---especially when typing with one hand. Too much tremor will cause motion blur in captured images and misalignment between frames, thus degrading the result.

Although our shoulder surfing system proves to be highly efficient against unprotected screens, there are some simple methods to mitigate this unique threat while not cumbering the user.

>>>>

\section{Limitations \& Discussions}
\label{sec-limitations-and-discussions}
There are certain limitations of this work. We require a certain degree of image capturing and processing abilities of the attacker's phone, and we also expect the victim not to exert too much disturbance to the target phone.

\vspace{1mm}
\noindent
\textbf{Image Capturing Ability}
Latest models of smartphones can capture images at 10 frames per second in burst mode easily, however, this ability is not common in phones that are 3 years old. Heavily used phones also perform less than ideal when capturing images in burst mode.

@@

\vspace{1mm}
\noindent
\textbf{Motion and Tremors}
In our experiment we assume the observed user will hold still his/her phone, and not making interactions too often. There might be extreme cases where frequent tilting of the screen may cause severe motion blur, degrading the result.

Although \textsf{SRPeek} proves to be highly efficient against unprotected screens, there are some simple methods to mitigate this unique threat while not cumbering the user.

### 2020-08-16 related_work.tex
9 pages

\subsection{Super Resolution}
Image SR is the process of reconstructing an image with a higher spatial resolution. Based on the structural pattern, self-similarity~\cite{suetake2008image}, or previous knowledge of the image genre, the single-image SR techniques take as input a single low-resolution image, rendering a sharp, high-resolution one by deducing missing information and reconstructing the missing pixels. Further, multi-image SR techniques work on a set of pictures on the same scene, such as multiple snapshots captured by a smartphone, successive images from a satellite, or adjacent frames on a video clip. These algorithms collect extra data from slight differences of these redundant images, often exhibiting better performance than single-image SR algorithms. And a variety of techniques have been proposed for the multi-image SR problem. And early works focus on the analysis of images in spatial or frequency domains. For example, the Shift-Add algorithm~\cite{farsiu2003robust} analyzes the spatial information by maximizing the pixel-wise possibility of high-resolution image from low-resolution images. Besides, approaches for the frequency domain rely on the Fourier transform of images. Assuming that the high-resolution scene is band-limited, these algorithms reconstruct high-frequency components from patterns of low-frequency components, removing bands of noise and blur effects simultaneously. Unfortunately, all SR techniques however, are subject-specific and achieve the best performance only for some contents, including natural photos, scanned text, satellite imaging, biometrics~\cite{Youm2016Image}
%\cl{more citation and table 1 row-3}
. While \textsf{SRPeek} can recover multi-type characters with complex strokes, including Chinese, English and numbers.

Deep learning approaches can also be adopted for Super Resolution. For example, SRCNN~\cite{dong2015image} was designed using CNN by replacing pooling layers with upsampling layers, achieving notably better performance than previous approaches. It however only focuses on single image SR, as the neural network accepts a single image as input. Besides, Generative Adversarial Networks (GAN) were also used to generate photo-realistic images~\cite{ledig2017photo}, with less artifacts and more genuine-looking details perceptible to the human eye. To resolve multi-image SR tasks, say video SR, existing works~\cite{shi2016real, kappeler2016video} design a structure similar to SRCNN, and accept complete video clips as input. Then the sequentiality and consistency between adjacent frames can help recover the missing pixels of clips using convolution networks, Specifically,
we can modify the dataflow to merge neighboring frames among the network layers~\cite{huang2017video}, or recurrently process the frames under the guidance of the output of the previous frame~\cite{sajjadi2018frame}. For images without consistency or sequential information, like satellite images, most works choose hybrid methods to solve the multi-image SR problem with multiple single-image SR procedures. They either merge the results of single-image SR algorithms for efficiency~\cite{kawulok2019deep}, or build a multi-image network to create a comprehensive view based on single image SR networks~\cite{8834937}. Due of the extreme blurriness of snapshots, these methods cannot deal with the new shoulder surfing threat model we proposed, which takes as input massive blurred snapshots without the consistency between frames. And they achieve limited performance, shown in Table~\ref{tbl:comparison}.

>>>>

\subsection{Super Resolution}
Image SR is the process of reconstructing an image with a higher spatial resolution. Based on the structural patternss, self-similarity~\cite{suetake2008image}, or previous knowledge of the image genre, the single-image SR techniques take as input a single low-resolution image, rendering a sharp, high-resolution one by deducing missing information and reconstructing the missing pixels. Further, multi-image SR techniques work on a set of pictures on the same scene, such as multiple snapshots captured by a smartphone, successive images from a satellite, or adjacent frames on a video clip. These algorithms collect extra data from slight differences of these redundant images, often exhibiting better performance than single-image SR algorithms.

Recent works on SR are mostly based on Convolutional Neural Networks(CNN)~\cite{dong2015image} and Generative Adversarial Networks(GAN)~\cite{ledig2017photo}, the former often gets closer to ground truth while the latter generates less artifacts and is more pleasing to the human eye. To resolve multi-image SR tasks, say video SR, some works~\cite{shi2016real, kappeler2016video} use 3 dimensional convolutions to utilize sequentiality and consistency between adjacent frames. Some works also modify the dataflow among the network layers to merge neighboring frames~\cite{huang2017video}, or recurrently process the frames under the guidance of the output of the previous frame~\cite{sajjadi2018frame}. For images without consistency or sequential information, like satellite images, most works choose hybrid methods, solving the multi-image SR problem with multiple single-image SR procedures. They either merge the results of single-image SR algorithms for efficiency~\cite{kawulok2019deep}, or build a multi-image network to create a comprehensive view based on single image SR networks~\cite{8834937}. Due of the extreme blurriness of snapshots, these methods cannot deal with the new shoulder surfing threat model we proposed, which takes as input massive blurred snapshots without the consistency between frames. And they achieve limited performance, shown in Table~\ref{tbl:comparison}.

### 2020-08-16 system_overview.tex
9 pages

\vspace{1mm}
\noindent
\textbf{Input:} Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen. Note that zooming is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if available, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range. This way information on the images will be more compact and easier to comprehend by neural networks.

\vspace{1mm}
\noindent
\textbf{Alignment:} The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will occasionally shift slightly across time due to the movements of its inner mechanism. Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images. The images are also spun to make the text horizontal in the process. The screen is cropped out and the rest of the image abandoned.

\vspace{1mm}
\noindent
\textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network. The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size (and the zooming of the camera lens in the Input phase will be adjusted accordingly).

\vspace{1mm}
\noindent
\textbf{Processing:} As our network accepts only 9x9 patches, we will process all the 9x9 patches among the input photo with our multi-frame super resolution network to generate 36x36 images (4x upscaling). The input is RGB colored, while the output, as we are not interested in color, is black and white. In this way, we generate upscaled image segments of all the characters on the target screen. The three calculation processes (Alignment, Adjustment, Processing) run parallel to the input process, so that once a batch of input images is available, they can be calculated and displayed on screen with a slight lag while the attacker can start to collect the next batch at the same time.

\vspace{1mm}
\noindent
\textbf{Output:} The outputs of our SR network, the 36x36 patches, are then merged into a whole. The overlapping pixels are thus processed: among all the outputs containing this pixel, we collect these values, remove outliers, and use their average as the result. As we only carve out the texts on the phone and process them, we will then insert these high-res texts back to their original locations on one of the input images, and display the patched image to the attacker (An illustration can be found in Fig.~\ref{illustration_of_system}).

These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of a few seconds. At critical times requiring continuous monitoring so as not to miss transient display, e.g. password entering, the system can simply lengthen the input phase across that period and process the data afterwards. The workflow of our system is shown in Figure~\ref{fig-workflow}.
\begin{figure}
  \centering
     \includegraphics[width=0.48\textwidth]{./pic/workflow_cl.pdf}
     \caption{Workflow of the \textsf{SRPeek} system.}
     \label{fig-workflow}
\end{figure}

>>>>

\vspace{1mm}
\noindent
\textbf{Input:} Under guidance of the attacker, The smartphone will zoom in, take focus, and take several images(the number is freely adjustable) with burst mode of the target screen. As digital zooming do not put in any extra data, we'll only use maximum optical zooming(if exist) when photographing to reduce the workload of neural networks.

\vspace{1mm}
\noindent
\textbf{Alignment:} The images are then aligned to mitigate tremors. Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images. The images are also spun to make the text horizontal in the process. The screen is cropped out and the rest of the image abandoned.

\vspace{1mm}
\noindent
\textbf{Adjustment:} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing to reduce the workload of the network. The characters are normally around 10x10 pixels, while variations in size aren't influential as they're covered in the training data, so zooming isn't necessary.

\vspace{1mm}
\noindent
\textbf{Processing:} As our SR network accepts only 9x9 patches, we will process all the 9x9 patches (with overlapping) among the input photo to generate 36x36 images (4x upscaling). The input is RGB colored, while the output, as we are not interested in color, is black and white. The three calculation processes (Alignment, Adjustment, Processing) run parallel to the input process, so that the attacker can process a batch of images while the next batch is being collected simultaneously.

\vspace{1mm}
\noindent
\textbf{Output:} The outputs of our SR network, the 36x36 overlapping patches, are then rearranged to their original locations and merged (using average values) into a single image. As we only carve out the texts for processing, we will then insert these high-res texts back to their original locations on one of the input images, and display the patched image to the attacker (An illustration of the patched image can be found in Fig.~\ref{illustration_of_system}).

These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of 1 to 2 seconds. At critical times requiring continuous monitoring so as not to miss transient display, e.g. password entering, the system can simply lengthen the input phase across that period and process the data afterwards. The workflow of our system is shown in Figure~\ref{fig-workflow}.
\begin{figure}
  \centering
     \includegraphics[width=0.90\linewidth]{./pic/workflow_cl.pdf}
     \caption{Workflow of the \textsf{SRPeek} system.}
     \label{fig-workflow}
\end{figure}
